D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-01-17 ootavacuous.tex
Fix side-effect issue
In expressions, multiple side effects is UB.  In parameter lists,
the order is unspecified.  So convert to parameter lists.

Reported-by: Stephen Dolan
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{quote}
	\co{y = ++i / ++i;} \\
	\co{x = y * z;}
\end{quote}

The standard does not specify the order of evaluation, so the resulting
value of \co{y} might be zero ($\frac{1}{2}$ truncated) or two
($\frac{2}{1}$).
In the former case, there is no semantic dependency from \co{z} to
\co{x}, but in the latter case there is.
Thus, semantic dependencies are not just a function of a particular
execution through the source code, but also of arbitrary choices made
by the C++ implementation.\footnote{
	Thanks to Peter Sewell for pointing out this possibility.}

>>>>

\begin{quote}
	\co{int foo(int a, int b)} \\
	\co{\{} \\
	\co{\ \ \ \ return a / b;} \\
	\co{\}} \\
	\\
	\co{y = foo(++i, ++i);} \\
	\co{x = y * z;}
\end{quote}

Because early C~implementers could not come to agreement, standard
does not specify the order of evaluation of function arguments, so the
resulting value of \co{y} might be zero ($\frac{1}{2}$ truncated) or two
($\frac{2}{1}$).
In the former case, there is no semantic dependency from \co{z} to
\co{x}, but in the latter case there is.
Thus, semantic dependencies are not just a function of a particular
execution through the source code, but also of arbitrary choices made
by the C++ implementation.\footnote{
	Thanks to Peter Sewell for pointing out this possibility.}
